Structured Versus Decorated Cospans

### 2021-04-08 cospans_new.tex
Added laxator and unit morphism diagrams to Theorem 2.4

\begin{proof}  See \cite[Theorem 4.2.1]{CourserThesis}. \end{proof}

>>>>

\begin{proof}  See \cite[Theorem 4.2.1]{CourserThesis}.

From the symmetric lax monoidal pseudofunctor $F \colon \A \to \Cat$, we can obtain a Beck-Chevalley symmetric monoidal opfibration $\Phi \colon (\A/U) \to \A$ as in \cref{thm:decorated_cospans_1}, where $U \colon \int F \to \A$ is the associated monoidal opfibration of the pseudofunctor $F$. We can do the same for the other symmetric lax monoidal pseudofunctor $F' \colon \A' \to \Cat$ to obtain another Beck-Chevalley symmetric monoidal opfibration $\Phi' \colon (\A'/U') \to \A'$.
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(\A/U)$};
\node (B) at (2,0) {$(\A'/U')$};
\node (C) at (0,-1.5) {$\A$};
\node (D) at (2,-1.5) {$\A'$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$\Phi$} (C)
(B) edge node[right]{$\Phi'$} (D)
(C) edge node[above]{$H$} (D);
\end{tikzpicture}
\]
We construct a strong monoidal functor $G \colon (\A/U) \to (\A'/U')$ between the monoidal comma categories $(\A/U)$ and $(\A'/U')$ that will make the induced square commute. Such a commutative square is a morphism in the 2-category $\mathbf{FMF}$ of monoidal bifibrations satisfying the Beck-Chevalley condition which then by a 2-functor $\mathbf{Fr} \colon \mathbf{FMF} \to \mathbf{FDbl}$ due to Shulman \cite[Theorem 14.11]{Shulman2008} will yield a map $$\mathbf{Fr}(G,H) \colon \mathbf{Fr}(\Phi) \to \mathbf{Fr}(\Phi')$$between the fibrant symmetric monoidal double categories $\mathbf{Fr}(\Phi)=F\lCsp$ and $\mathbf{Fr}(\Phi')= F'\lCsp$.

The monoidal comma category $(\A/U)$ has:
\begin{enumerate}
\item{objects as triples $(a,x,a \to U(x))$, and}
\item{a morphism from $(a,x,a \to U(x))$ to $(b,y,b \to U(y))$ is a pair of morphisms $f \colon a \to b$ and $\tau \colon x \to y$ that make the following square commute:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$b$};
\node (C) at (0,-1) {$U(x)$};
\node (D) at (1,-1) {$U(y)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$f$} (B)
(A) edge node[left]{$$} (C)
(B) edge node[right]{$$} (D)
(C) edge node[above]{$U(\tau)$} (D);
\end{tikzpicture}
\]
}
\end{enumerate}
The tensor product of two objects $(a_1,x_1,a_1 \to U(x_1))$ and $(a_2,x_2,a_2 \to U(x_2))$ is given by $$(a_1,x_1,a_1 \to U(x_1)) \otimes (a_2,x_2,a_2 \to U(x_2)) = (a_1+a_2,x_1+x_2,a_1+a_2 \to U(x_1+x_2)).$$The monoidal unit of $(\A/U)$ is given by $(0_\A,0_\X,0_\A \to U(0_\X))$. Those of $(\A'/U')$ are analogous.

On objects, the strong monoidal functor $F \colon (\A/U) \to (\A'/U')$ is defined as follows:
\begin{enumerate}
\item{given $(a,x,a \to U(x))$ in $(\A/U)$, $$G(a,x,a \to U(x)) = (H(a),\theta_m E(x) \phi,H(a) \to U'(\theta_m E(x) \phi))$$where if $1 \xrightarrow{x} F(m)$, then $U(x)=m$ and $\theta_m E(x) \phi$ is given by 
$$1 \xrightarrow{\phi} E(1) \xrightarrow{E(x)} E(F(m)) \xrightarrow{\theta_m} F'(H(m))$$
so that $U'(\theta_m E(x) \phi)=H(m)$, }
\item{given a pair of morphisms $(f,\tau)$ that make the following square commute:
\node (C) at (0,-1) {$U(x)$};
\node (D) at (1,-1) {$U(y)$};
(A) edge node[left]{$$} (C)
(B) edge node[right]{$$} (D)
(C) edge node[above]{$U(\tau)$} (D);
we define $$G(f,\tau)=(H(f),\theta_h E(\tau) \phi).$$
which make the following square in $(\A'/U')$ commute:
\node (A) at (0,0) {$H(a)$};
\node (B) at (3,0) {$H(b)$};
\node (C) at (0,-1) {$U'(\theta_m E(x) \phi)$};
\node (D) at (3,-1) {$U'(\theta_n E(y) \phi))$};
(A) edge node[above]{$H(f)$} (B)
(A) edge node[left]{$$} (C)
(B) edge node[right]{$$} (D)
(C) edge node[above]{$U'(\theta_h E(\tau) \phi)$} (D);
where $\tau$ and $\theta_h E(\tau) \phi$ are given respectively by:
(G) edge node [below] {$y$} (I)
(D) edge node [above] {$\theta_n$} (F)
(L) edge node[below]{$E(y)$} (D)
(B) edge node[right]{$E(F(h))$} (D);
\end{enumerate}
The laxator is given by the following natural isomorphism between $\theta_m E(x) \phi + \theta_n E(y) \phi$ and $\theta_{m+n} E(x+y) \phi$:
\hspace{-.6in}
\node () at (3,-0.5) {$\scriptscriptstyle{\stackrel{E_{x_1,x_2}} \cong}$};
\node () at (1.25,-0.5) {$\scriptscriptstyle{\stackrel{\lambda} \cong}$};
\node (L1) at (0.5,0) {$\scriptscriptstyle{1 \times E(1)}$};
\node (L2) at (0.5,-1) {$\scriptscriptstyle{E(1)}$};
\node (K) at (-1,0) {$\scriptscriptstyle{1 \times 1}$};
\node (K2) at (-1,-1) {$\scriptscriptstyle{1}$};
\node (B) at (2,0) {$\scriptscriptstyle{E(1) \times E(1)}$};
\node (D) at (2,-1) {$\scriptscriptstyle{E(1 \times 1)}$};
\node (E) at (4,0) {$\scriptscriptstyle{E(F(m)) \times E(F(n))}$};
\node (F) at (4,-1) {$\scriptscriptstyle{E(F(m) \times F(n))}$};
\node (G) at (7,0) {$\scriptscriptstyle{F'(H(m)) \times F'(H(n))}$};
\node (H) at (10,0) {$\scriptscriptstyle{F'(H(m)+H(n))}$};
\node (I) at (7,-1) {$\scriptscriptstyle{E(F(m+n))}$};
\node (J) at (10,-1) {$\scriptscriptstyle{F'(H(m+n))}$};
(K) edge node [left] {$\lambda$} (K2)
(K) edge node [above] {$1 \times E_0$} (L1)
(K2) edge node [above] {$E_0$} (L2)
(H) edge node [right] {$F'(H_{m,n})$} (J)
(E) edge node [above] {$\theta_m \times \theta_n$} (G)
(G) edge node [above] {$\phi'_{H(m),H(n)}$} (H) 
(F) edge node [above] {$E(\phi_{m,n})$} (I)
(I) edge node [above] {$\theta_{m+n}$} (J)
(B) edge node [above] {$E(x) \times E(y)$} (E)
(D) edge node [above] {$E(x \times y)$} (F)
(E) edge node [right] {$E_{F(m),F(n)}$} (F)
(L1) edge node[above]{$E_0 \times 1$} (B)
(L1) edge node [left] {$\lambda$} (L2)
(L2) edge node[above]{$E(\lambda^{-1})$} (D)
(B) edge node[right]{$E_{1,1}$} (D);
and we also have a natural isomorphism between $0_{\inta F'}$ and $G(0_{\inta F})$ given by:
\node (A) at (-1,0.5) {$\scriptscriptstyle{1}$};
\node () at (4,0.66) {$\scriptscriptstyle{\cong}$};
\node (A1) at (0,0) {$\scriptscriptstyle{E(1)}$};
\node (A2) at (2,0) {$\scriptscriptstyle{E(F(0_\A))}$};
\node (A3) at (4,0) {$\scriptscriptstyle{E(F(0_\A))}$};
\node (A4) at (6,0) {$\scriptscriptstyle{F'(H(0_\A))}$};
\node (A') at (2,0.5) {$\scriptscriptstyle{F'(H(0_\A))}$};
\node (B1) at (0,1) {$\scriptscriptstyle{F'(0_{\A'})}$};
\node (B2) at (6,1) {$\scriptscriptstyle{F'(0_{\A'})}$};
(A) edge node [below] {$\scriptscriptstyle{E_0}$} (A1)
(A) edge node [above] {$\scriptscriptstyle{\phi_0'}$} (B1)
(A1) edge node [above] {$\scriptscriptstyle{E(\phi_0)}$} (A2)
(A2) edge node [above] {$\scriptscriptstyle{E(F(!_{0_\A}))}$} (A3)
(A3) edge node [below] {$\scriptscriptstyle{\theta_{0_\A}}$} (A4)
(A2) edge node [left] {$\scriptscriptstyle{\theta_{0_\A}}$} (A')
(B1) edge node [fill=white] {$\scriptscriptstyle{F'(H_0)}$} (A')
(A') edge node [fill=white] {$\scriptscriptstyle{F'(H(!_{0_\A}))}$} (A4)
(B2) edge node [right] {$\scriptscriptstyle{F'(H_0)}$} (A4)
(B1) edge node [above] {$\scriptscriptstyle{F'(!_{0_{\A'}})}$} (B2);
One can show that this laxator and unit morphism satisfy the four required coherence laws of a symmetric strong monoidal functor.
